A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-01-05 paper/draft.tex
fix bibliography
edit intro
analyze further the differential compensation

>>>>

\section{Introduction}
\label{sec:intro}

How does

Literature on patronage and selection: \citet{robinson2013political}. Extant literature on selection of public officials have primarily focused on who becomes a politician \citet{dal2017becomes}. There remains unanswered questions regarding who enters the bureaucracy, what types of employment they held, and what are the differential compensations among public officials.

In this paper, I leverage micro-level partisan information with employment data to assess the degree to which there are differential compensation structures and differences in observables among partisan and non-partisan. What I find is that the benefits of public secotr employment do not accrue to poorer voters. Rather

\section{Context and Data}
\label{sec:context}

\section{Empirical strategy}
\label{sec:empirical}

\section{Conclusion}
\label{sec:conclusion}

\bibliography{patronage}
